{\LARGE On the Use of Generic Types for Smart Contracts}

### 2022-03-05 cluster_computing/010_introduction.tex
cover letters + biogra

This paper is a revised and extended version of~\cite{BeniniGMS21}.
In comparison to that paper, Sec.~\ref{sec:takamaka} and
Sec.~\ref{sec:validators} are new; while all other sections have been expanded and the enriched with several explanatory figures.

>>>>

This paper is a revised and extended version of~\cite{BeniniGMS21}.
In comparison to that paper, Sec.~\ref{sec:takamaka} and
Sec.~\ref{sec:validators} are new; while all other sections have been expanded with several additional details and enriched with many explanatory figures.
